Coherent optical association of a single molecule

### 2020-09-24 paper.tex
Update on Overleaf.

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}.

To obtain the full picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM). As shown in figure ~\ref{f-theory}, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states. For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus %Since for a typical molecular potential the spacing between states
%decreases with increasing vibrational levels,
%a weakly bound excited molecular state
limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning. Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
% This further increases the scattering rate for a weakly bond excited state.
Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....),
we found a distinct optimal regime from what has been explored experimentally previously. Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state. As a result, we use a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition. (mention the trend, also v=12 will work as similarly as v=0)

>>>>

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency, but such choice of state also increases the scattering during the transfer process to render it incoherent, resulting in molecule loss~\cite{Wynar2000,Rom2004}. For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning. Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state has strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

To obtain the full picture, we perform a full calculation of the Raman Rabi frequency and scattering rate at different detunings (full result in SM). As shown in figure ~\ref{f-theory}, the ratio of the Raman Rabi rate to scattering rate can be made better for more deeply bound states compared to weakly bound states.  %Since for a typical molecular potential the spacing between states
%decreases with increasing vibrational levels,
%a weakly bound excited molecular state

% This further increases the scattering rate for a weakly bond excited state.
Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....),
we found a distinct optimal regime from what has been explored experimentally previously. Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state. As a result, we use a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) to drive the Raman transition. (mention the trend, also v=12 will work as similarly as v=0)
